Week2 - Descriptives

### 2024-09-11 RQdraft1.Rmd
updatedmenusweek2
usingrefsandnotes

---
title: "RQdraft1"
author: "Vero"
date: "2024-09-10"
output: html_document
---

@@

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```
# Brainstorm
- Journal prestige 
- Gender homphily 
- Age 
- repeated publications 
- nr of publications
- Dutch or English text publications
- gender segregation and field of publication (journal field)

---

# Research Questions
RQ1a: 
  To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Computing Sciences at Radboud University?

@@

## Horta et al. (2022)
- male researchers preferred to co-publish with other male researchers, 
- and female researchers preferred to collaborate with other females.
- researchers of approximately similar ages tended to collaborate more with each other.
- geographical, cultural, & institutional proximity were strongest predictors of collaboration.
- analysis shows that in the social sciences, ACQUIRED attributes (particularly preferences regarding research agendas) take precedence over ASCRIBED attributes (e.g. gender or age)

- Horta et al. (2022) - RQs:
  - (1) What homophily preferences determine research collaborations among higher education researchers? 
  - (2) What are the most powerful homophily indicators in research collaborations in higher education research?

## Kwiek & Roszka (2021)
- Most male scientists collaborate solely with males.
- Most female scientists, in contrast, do not collaborate with females at all.
- All-female authorship marginal, all-male authorship pervasive, in all age groups.
- Articles written in mixed-sex collaboration published in more prestigious journals.

---

@@

Horta, H., Feng, S., & Santos, J. M. (2022). Homophily in higher education research: a perspective based on co-authorships. Scientometrics, 127(1), 523–543. https://doi.org/10.1007/s11192-021-04227-z

Kwiek, M., & Roszka, W. (2021). Gender-based homophily in research: A large-scale study of man-woman collaboration. Journal of Informetrics, 15(3), 101171. https://doi.org/10.1016/j.joi.2021.101171

-

>>>>

---
title: "RQdraft1"
author: "Verooo"
date: "2024-09-10"
output: html_document
---

@@

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

# Brainstorm

-   Journal prestige
-   Gender homphily
-   Age
-   repeated publications
-   nr of publications
-   Dutch or English text publications
-   gender segregation and field of publication (journal field)

------------------------------------------------------------------------

# Research Questions

**RQ1a:**

To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University?

@@

## Horta et al. (2022)

-   male researchers preferred to co-publish with other male researchers,

-   and female researchers preferred to collaborate with other females.

-   researchers of approximately similar ages tended to collaborate more with each other.

-   geographical, cultural, & institutional proximity were strongest predictors of collaboration.

-   analysis shows that in the social sciences, ACQUIRED attributes (particularly preferences regarding research agendas) take precedence over ASCRIBED attributes (e.g. gender or age)

-   Horta et al. (2022) - RQs:

    1.  What homophily preferences determine research collaborations among higher education researchers?

    ```{=html}
    <!-- -->
    ```
    2.  What are the most powerful homophily indicators in research collaborations in higher education research?

## Kwiek & Roszka (2021)

-   Most male scientists collaborate solely with males.
-   Most female scientists, in contrast, do not collaborate with females at all.
-   All-female authorship marginal, all-male authorship pervasive, in all age groups.
-   Articles written in mixed-sex collaboration published in more prestigious journals.

------------------------------------------------------------------------

@@

Horta, H., Feng, S., & Santos, J. M. (2022). Homophily in higher education research: a perspective based on co-authorships. Scientometrics, 127(1), 523–543. <https://doi.org/10.1007/s11192-021-04227-z>

Kwiek, M., & Roszka, W. (2021). Gender-based homophily in research: A large-scale study of man-woman collaboration. Journal of Informetrics, 15(3), 101171. <https://doi.org/10.1016/j.joi.2021.101171>

### 2024-09-11 RQdraft2.Rmd
usingrefsandnotes

---
title: "RQdraft1"
author: "Verooo"
date: "2024-09-10"
output: html_document
---

@@

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

# Brainstorm

-   Journal prestige
-   Gender homphily
-   Age
-   repeated publications
-   nr of publications
-   Dutch or English text publications
-   gender segregation and field of publication (journal field)

------------------------------------------------------------------------

# Research Questions

**RQ1a:**

To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University?

@@

-   (1a+b needed? Would like more concise, not ask uneccessary questions)
-   (2&3 seem random and disconnected; Journal prestige of interest tho, how to best include?)
-   (necessity to have RQ3 that asks about structural networks effects?)

## Horta et al. (2022)

-   male researchers preferred to co-publish with other male researchers,

-   and female researchers preferred to collaborate with other females.

-   researchers of approximately similar ages tended to collaborate more with each other.

-   geographical, cultural, & institutional proximity were strongest predictors of collaboration.

-   analysis shows that in the social sciences, ACQUIRED attributes (particularly preferences regarding research agendas) take precedence over ASCRIBED attributes (e.g. gender or age)

-   Horta et al. (2022) - RQs:

    1.  What homophily preferences determine research collaborations among higher education researchers?

    ```{=html}
    <!-- -->
    ```
    2.  What are the most powerful homophily indicators in research collaborations in higher education research?

## Kwiek & Roszka (2021)

-   Most male scientists collaborate solely with males.
-   Most female scientists, in contrast, do not collaborate with females at all.
-   All-female authorship marginal, all-male authorship pervasive, in all age groups.
-   Articles written in mixed-sex collaboration published in more prestigious journals.

------------------------------------------------------------------------

@@

Horta, H., Feng, S., & Santos, J. M. (2022). Homophily in higher education research: a perspective based on co-authorships. Scientometrics, 127(1), 523–543. <https://doi.org/10.1007/s11192-021-04227-z>

Kwiek, M., & Roszka, W. (2021). Gender-based homophily in research: A large-scale study of man-woman collaboration. Journal of Informetrics, 15(3), 101171. <https://doi.org/10.1016/j.joi.2021.101171>

>>>>

---
title: "RQdraft2"
author: "Verooo"
date: "2024-09-11"
output: html_document
---

@@

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```
# Brainstorm

---

# Research Questions (old, replace with new ones!)
RQ1a: 
  To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University?

@@

## Horta et al. (2022)
- male researchers preferred to co-publish with other male researchers, 
- and female researchers preferred to collaborate with other females.
- researchers of approximately similar ages tended to collaborate more with each other.
- geographical, cultural, & institutional proximity were strongest predictors of collaboration.
- analysis shows that in the social sciences, ACQUIRED attributes (particularly preferences regarding research agendas) take precedence over ASCRIBED attributes (e.g. gender or age)

- Horta et al. (2022) - RQs:
  - (1) What homophily preferences determine research collaborations among higher education researchers? 
  - (2) What are the most powerful homophily indicators in research collaborations in higher education research?

## Kwiek & Roszka (2021)
- Most male scientists collaborate solely with males.
- Most female scientists, in contrast, do not collaborate with females at all.
- All-female authorship marginal, all-male authorship pervasive, in all age groups.
- Articles written in mixed-sex collaboration published in more prestigious journals.

---

@@

Horta, H., Feng, S., & Santos, J. M. (2022). Homophily in higher education research: a perspective based on co-authorships. Scientometrics, 127(1), 523–543. https://doi.org/10.1007/s11192-021-04227-z

Kwiek, M., & Roszka, W. (2021). Gender-based homophily in research: A large-scale study of man-woman collaboration. Journal of Informetrics, 15(3), 101171. https://doi.org/10.1016/j.joi.2021.101171

### 2024-09-11 week2.Rmd
usingrefsandnotes

@@

```{r}
# 003
# A,B,C, the empty graph.

@@

@@

# assignment: give (on ego level) descriptive statistics on all kind of centrality measures

>>>>

# Triads - 4x4 matrix

@@

## Triad census output

```{r}

# 003
# A,B,C, the empty graph.

@@

# heading (learning to take notes with R)

note:

1.  kjhg\
2.  lkjh
    -   kjh
    -   kjhgf

text here \$ N = ß \Sigma lss \sqrt {sd } \$ text again

# Centrality measures (practice with a network)

@@

sna::triad.census(tenxten)

# Nr. of possible Triad compositions:
  # 10*9*8 / 6 =

# Play around with Centrality Measures 
```

# START WRITING INTRO (UPDATE RESEARCH QUESTIONS)

Try to be specific show that you UNDERSTAND INTER-DEPENDENCIES

MAKE A LISTOFTHE TYPE OF DATA YOU WILL NEED Relational attributes, etc.

Update Lab journal

[USING THE REFERENCES]{.underline}

Open: references.bib take "bibTex Citation" if you want to use it, use \@ - symbol and use the word behind the { \
In this example, it would be \@ "rmarkdown2018" (without the quotation marks

@Book{rmarkdown2018, title = {R Markdown: The Definitive Guide}, author = {Yihui Xie and J.J. Allaire and Garrett Grolemund}, publisher = {Chapman and Hall/CRC}, address = {Boca Raton, Florida}, year = {2018}, note = {ISBN 9781138359338}, url = {<https://bookdown.org/yihui/rmarkdown>}, }
